Computer Science House Constitution

### 2024-01-30 constitution.tex
Update #41 Review Responsibilities of the Social Director (#63)
* Update 5.C.4 per Discussion

* reverted socials responsibilities to two bullet points with added clarification

---------

Co-authored-by: Jeremy Smart <jeremy3141592@gmail.com>

\asubsection{Responsibilities of the Social Director(s)}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House activities and events
	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
	\item To vote on issues presented to the Executive Board
\end{enumerate}

>>>>

\asubsection{Responsibilities of the Social Director(s)}
\begin{enumerate}
	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
	\item To exercise general supervision over Social operations
	\item To oversee the organization, initiation, and execution of House social activities
  \item To ensure that there is a variety of events for House members to participate in throughout the academic year
\end{enumerate}
